intRo

### 2015-07-15 jsm-2015/eric/index.Rmd
Cut out parts that wont be said

# First look | http://intro-stats.com

@@

## `intRo` in the wild
 - `intRo` will be used this semester in STAT 201
      - Homework assignments and labs will use `intRo` to emphasize class concepts
 - `intRo` is a supplement, not the focus of the class

@@

# Our turn

@@

## Consistent UI (Cont'd)
 - Large, easy to click icons in the page header to help students find
exactly what they need easily
 - Each module maintains a consistent layout, helping the user to become familiar with the location of the options, the results, and the code
 - Documentation website that is consistent with
the interface of the application; covers all default modules and makes learning to use `intRo` even more painless

@@

## Modularity (Cont'd)
The interface is created with the following statement

```{r, tidy=FALSE, eval=FALSE}
## Source ui
module_info <- read.table("modules/modules.txt", header = TRUE, 
                          sep=",")
sapply(file.path("modules", dir("modules")[dir("modules") 
                      != "modules.txt"], "ui.R"), source)
## Create the UI
shinyUI(navbarPage("intRo", theme = "bootstrap.min.css",
               tabPanel(title="", icon=icon("home"),
                        fluidRow(
                        ### <b>
                          do.call(navlistPanel, 
                              c(list(id = "side-nav", 
                              widths = c(2, 10)), mylist))
                        ### </b>
                        )
               ), ...
))
```

## Modularity (Cont'd)
The server functions are dynamically generated using a similar method

```{r, eval=FALSE, tidy=FALSE}
shinyServer(function(input, output, session) {
  ## Module info
  module_info <- read.table("modules/modules.txt", 
                            header = TRUE, sep=",")
  ## Modules
  types <- c("helper.R", "static.R", "observe.R", 
             "reactive.R", "output.R")
  modules_tosource <- file.path("modules", 
                                apply(expand.grid(
                                module_info$module, types)
                                , 1, paste, collapse = "/"))
  ## Source the modules
  for (mod in modules_tosource) {
    ### <b>
    source(mod, local = TRUE) 
    ### </b>
  }
})
```

# Challenges

## Tradeoffs
We encountered a number of challenges in striving to strike the balance of functionality and ease-of-use:

 - Storing the user's results
 - Presenting only relevant options to the user
 - Producing clean and executable R code

## Storing results
 - Users must be able to print results, but only the results they want
 - Reactivity makes this somewhat challenging

**Solution**: Store Buttons

<img src="images/store.png" height="300"></img>

## Storing results (Cont'd)
 - Each module contains, at the bottom, a Store button
 - When Store is pressed, code is stored in code panel
     - Additional challenge: All options selected must also be stored!
 - When user goes to print results, only this particular code is executed

## Presenting choices
 - `intRo` is flexible, but must also be simple for the introductory student
 - Despite increasing the complexity of the code, we decided to only show options appropriate for the given selections.

**Example**:

<img src="images/graphical.png" height="300">

## Presenting choices (Cont'd)
<img src="images/graphical_table.png">

## Producing clean code
Code generated must be:

 - Executable on the server
 - Executable on the user's machine
 - Clean

## Producing clean code (Cont'd)
But how do we handle uploaded data?

```{r, eval=FALSE}
file.choose <- function () {
    return(input$data_own[,"datapath"])
}
```

Now we can provide to the user *and* the server:

```{r, eval=FALSE}
intro.data <- read.csv(file.choose())
```

>>>>

@@

## `intRo` in the wild
 - `intRo` was used last semester at Iowa State University in STAT 201
      - Homework assignments and labs used `intRo` to emphasize class concepts
 - `intRo` is a supplement, not the focus of the class

@@

# Live Demo

@@

@@
